---
title: "Data types"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Data elements
The term refers to the type of a particular element. The types in question are numerical, integer, complex, logical and character.

```{r, results='hold'}
x <- 1 ##This is a typical integer value
y <- 1.3 ##This is a typical numerical value
z <- 1 + 2i ##This is a typical complex value
d <- TRUE ##This is a typical logical value
f <- "Blergh" ##This is a typical character value
```

###Variables
Variables can be defined with <- and ->, depending on when in a line the definition takes place. For example:

```{r, results='hold'}
x <- 1 + 1
2 + 2 -> y
```

###Vectors
A vector is a sequence of data elements (or components) of the same type. When a vector is defined that holds data elements of various types, the vector coerces all the components to character values. [More about vectors](vector.html)

```{r, results='hold'}
x <- c(1, 2, 3)
y <- c("a", "b", "c")
z <- c(TRUE, FALSE, TRUE)
z2 <- c(T, F, T)
y2 <- c(1 + 2i, 2 + 1i, 3 + 5i)
mix <- c(1, "b", TRUE, 1 + 2i)
class(mix)
```

###Data Frames
Data frames are used to store tables of data. Those tables are lists of vectors of the same length.

```{r, results='hold'}
x <- c(1.3, 2.4, 3.5) ##This is a vector with numericals.
y <- c(TRUE, TRUE, FALSE) ##This is a vector with logicals.
z <- c("Character!", "Values!", "Rock!") ##This is a vector of character values.
df <- data.frame(x, y, z) ##This is a data frame that includes the x, y and z's.
df
```

###Lists
A list is a vector that can contain other objects, just like vectors, but also including other vectors, data frames, etc.

```{r, results='hold'}
x <- c(1.3, 2.4, 3.5) ##This is a vector with numericals.
y <- c(TRUE, TRUE, FALSE, NA) ##This is a vector with logicals and an NA.
z <- "Character!" ##This is a single character value.
l <- list(x, y, z) ##This is a list that includes the x, y and z's.
l
```

###Matrices
A matrix is a two-dimensional layout of data elements of the same type. [More about matrices](matrix.html)

```{r, results='hold'}
A <- matrix(  ##Define matrix. Usually matrices are indicated with CAPITALS.
  c(1, 2, 3, 4, 5, 6), ##Define the values to be held by the matrix.
  nrow = 2, ##number of rows
  ncol = 3, ##number of columns
  byrow = TRUE) #How to fill the matrix with the defined values.
A
```

###Arrays
An array is a data object that can hold data in more than two dimensions. For example, an array of the size 2 x 2 x 4 would be four 2 x 2 matrices stacked up on each other. [More about arrays](array.html)

```{r, results = 'hold'}
x <- c(1, 2, 3, 4)
y <- c(4, 5, 6, 7)
z <- c(7, 8, 9, 10)
array <- array(c(x, y, z), dim = c(2, 2, 3)) ##The array takes the three vectors in, the dim parameter defines the dimensions of the array as 2 x 2 x 3
array
```
----
[LICENSE: CC-BY-SA-4.0](LICENSE) // [BACK TO INDEX](index.html)