---
title: "Data types"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Data elements
The term refers to the type of a particular element. The types in question are numerical, integer, complex, logical and character.

```{r, results='hold'}
x <- 1 ##This is a typical integer value
y <- 1.3 ##This is a typical numerical value
z <- 1 + 2i ##This is a typical complex value
d <- TRUE ##This is a typical logical value
f <- "Blergh" ##This is a typical character value
```

###Variables
Variables can be defined with <- and ->, depending on when in a line the definition takes place. For example:

```{r, results='hold'}
x <- 1 + 1
2 + 2 -> y
```

###Vectors
A vector is a sequence of data elements (or components) of the same type. When a vector is defined that holds data elements of various types, the vector coerces all the components to character values.

```{r, results='hold'}
x <- c(1, 2, 3)
y <- c("a", "b", "c")
z <- c(TRUE, FALSE, TRUE)
z2 <- c(T, F, T)
y2 <- c(1 + 2i, 2 + 1i, 3 + 5i)
mix <- c(1, "b", TRUE, 1 + 2i)
class(mix)
```

###Data Frames

###Matrices

###Lists

----
[LICENSE: CC-BY-SA-4.0](LICENSE)