---
title: "Vectors"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Making a vector.
Here are a few examples of a vector being defined. We're skipping assigning them to a variable to provide an immediate printout.

```{r, results='hold'}
x <- c(1, 2, 3, 4, 5) ##Creates the elements 1, 2, 3, 4 and 5.
x <- seq(1:5) ##Creates a sequence from 1 to (and including) 5.
x <- seq(1, 5, length = 10) ##Creates a sequence of 10 steps from 1 to (and including) 5.
x <- rep(1, 10) ##Creates a sequence of ten ones.
x <- rep(c(1, 2, 3), 3) ##Creates a sequence that's composed of 1, 2, 3, three times over.
x <- rep(c(1, 2, 3), each = 4) ##Creates a sequence that has four ones, four twos and four threes.
x <- rnorm(5) ##Creates a vector containing 5 elements with random variables from the normal distribution.
```

###Working with vectors.
Here are code examples for a few methods that can be used on vectors.
```{r, results='hold'}
x <- (c(seq(1:10), 6, 11, 13)) ##An example vector that contains the values from 1 to 10 plus a few others.
length(x) ##Returns a value corresponding to the number of values within the vector.
sort(x) ##Returns the vector sorted from lowest to highest.
sort(x, decreasing = TRUE) ##Returns the vector sorted from highest to lowest.
rank(x) ##Returns the rank of each element of the vector, that is to say, where it'd get positioned were it to be sorted.
order(x) ##Returns a list of in which order the elements would be positioned, were they to get sorted.
mean(x) ##Displays the mean of the values in the vector.
median(x) ##Displays the median value of a vector.
quantile(x) ##Displays sample quantiles from the vector.
```

###Manipulating vectors
Sometimes we need to put vectors together, or add them into data tables and so fourth. Here are some examples of how to do that.

```{r, results='hold'}
c(x, x) ##Joins two vectors into a longer vector
c(x, x, x) ##Joins twi vectors into a longer vector, aaaand so on..
cbind(x, x) ##Joins two vectors together as columns in a matrix.
rbind(x, x) ##Joins two vectors together as rows in a matrix.
```



----
[LICENSE: CC-BY-SA-4.0](LICENSE) // [BACK TO INDEX](index.html)